%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full stack software engineer} % Job title
    {Pinna d.o.o.} % Organization
    {Maribor, Slovenia} % Location
    {Okt. 2016 - ongoing} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Colaborated with remote teams implementing products that 
        target the healthcare system and are being used in healthcare
         provider systems and clinical centers in the country.}
        \item {Helped designing an overall service architecture 
        and coding guidelines for designing micro-services in the company.}
        \item {Designed communication strategies between micro-services 
        using event sourcing and CQRS using the domain driven design principles.}
        \item {Implemented several API microservices in .NET Framework and Core.}
        \item {Deployed a centralized code quality metrics environment 
        (Sonarqube) that analyzes code and provides information and 
        warnings about code smells and bad coding practices.}
        \item {Designed and implemented a system that records audio 
        dictations on mobile devices and communicates with a web 
        service which in term communicates with desktop applications,
         bridging the central systems and the mobile devices in a secure manner.}
      \end{cvitems}
    }
    \cventry
    {DevOps engineer} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built fully automated CI/CD pipelines on Azure
         DevOps for containerized applications using Docker with local 
         and Azure cloud deployments .}
        \item {Utilized scripting tools such (Cake Build, DevOps yaml) 
        ensuring CI pipelines use code from source control for running builds.\\}
      \end{cvitems}
    }
    \cventry
    {Systems engineer} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Configured the infrastructure needed to deploy, 
        and run services in multiple parallel sandboxed environments 
        and in production.}
        \item {Leveraged the services and infrastructure provided as a
         part of the Azure stack including (but not limited to) 
         docker containers, VM's, Azure Service Bus, Web Apps and Azure AD.\\}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder \& Software Engineer} % Job title
    {Trivia, programske rešitve s.p.} % Organization
    {Maribor, Slovenia} % Location
    {Aug. 2014 - Okt. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed micro-services that communicated with the 
        government's web services (davčne blagajne) REST API.}
        \item {Developed software from design to production phase for 
        mobile cash registers used in coffe shops in the country.}
        \item {Developed a web based resource management system used 
        for automating ordering goods on a massive scale from multiple 
        suppliers while calculating ensuring optimal price ratios.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
